The Emergent Simplicity of Galaxy Size

### 2017-09-29 paper/galsize_paper.tex
Updated models section with subsections

%%%%%%%%  halo properties  %%%%%%%%
\newcommand{\halospin}{\lambda_{\rm halo}}
\newcommand{\mvir}{M_{\rm vir}}
\newcommand{\macc}{M_{\rm acc}}
\newcommand{\mpeak}{M_{\rm peak}}
\newcommand{\zpeak}{z_{\rm peak}}
\newcommand{\mhalo}{M_{\rm halo}}
\newcommand{\rvir}{R_{\rm vir}}
\newcommand{\rmpeak}{R_{\rm M_{peak}}}

@@

@@

\beq
\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak)
\eeq

When generating Monte Carlo realizations of our model galaxy sizes, we add log-normal scatter $\sigmarhalf=0.2$ dex. For some models explored in this work, this scatter will be purely stochastic, while other models will introduce a correlation between the scatter and an additional halo property. Models employing correlated scatter are implemented using the {\tt halotools.empirical\_models.conditional\_abunmatch} function, which generalizes the Conditional Abundance Matching technique described in \citet{hearin_etal13b}.

>>>>

%%%%%%%%  halo properties  %%%%%%%%
\newcommand{\halospin}{\lambda_{\rm halo}}
\newcommand{\mvir}{M_{\rm vir}}
\newcommand{\macc}{M_{\rm acc}}
\newcommand{\mpeak}{M_{\rm peak}}
\newcommand{\zpeak}{z_{\rm peak}}
\newcommand{\mhalo}{M_{\rm halo}}
\newcommand{\rvir}{R_{\rm vir}}
\newcommand{\rmpeak}{R_{\rm M_{peak}}}
\newcommand{\vmaxmpeak}{V_{\rm peak}}

@@

In \S\ref{sec:results}, we calculate predictions for the $\rhalf-$dependence of galaxy clustering for several different kinds of empirical models, described in turn below.

\subsubsection{K13 model}
\label{subsubsec:k13model}

@@

\beq
\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak)
\eeq
When generating predictions for the K13 model galaxy sizes, we add uncorrelated log-normal scatter of $\sigmarhalf=0.2$ dex to generate a Monto Carlo realization of the model population.

\subsubsection{K13 + co-evolution model}
\label{subsubsec:coevolutionmodel}

The {\em K13 + co-evolution model} model is identical to K13, but the scatter in $\rhalf$ at fixed $\rmpeak$ is no longer purely stochastic, but is instead correlated with $\vmaxmpeak.$

 stochastic, while other models will introduce a correlation between the scatter and an additional halo property. Models employing correlated scatter are implemented using the {\tt halotools.empirical\_models.conditional\_abunmatch} function, which generalizes the Conditional Abundance Matching technique described in \citet{hearin_etal13b}.

\subsubsection{K13 + stripping model}
\label{subsubsec:strippingmodel}
